Retrofitting Effect Handlers onto OCaml

### 2020-11-20 retro-concurrency.tex
Less detail on core count and cache for machine spec in evaluation section; put in reference link for the processor

In this section, we evaluate the performance of Multicore OCaml effect handlers
against the performance requirements set in \S\ref{sec:req}. Multicore OCaml is
an extension of the 4.10.0 OCaml compiler with support for shared memory
parallelism and effect handlers. These results were obtained on a 2-socket,
Intel\textregistered Xeon\textregistered Gold 5120 x86-64 server, with 28
physical cores (14 cores on each socket), and 2 hardware threads per core. Each
core runs at 2.20GHz and has 32 KB of L1 data cache, 32 KB of L1 instruction
cache and 1MB of L2 cache. The cores on a socket share a 19.25 MB L3 cache. The
server has 64GB of main memory and runs Ubuntu 18.04.

>>>>

In this section, we evaluate the performance of Multicore OCaml effect handlers
against the performance requirements set in \S\ref{sec:req}. Multicore OCaml is
an extension of the 4.10.0 OCaml compiler with support for shared memory
parallelism and effect handlers. These results were obtained on a 2-socket
Intel\textregistered Xeon\textregistered Gold 5120
x86-64~\cite{IntelXeonGold5120Spec} server running Ubuntu 18.04 with 64GB of main
memory.
